Synthesis of Solar Photovoltaic Systems: Optimal Sizing Comparison\thanks{Supported by Newton Fund (ref. 261881580) and FAPEAM (Amazonas State Foundation for Research Support, calls 009/2017 and PROTI Pesquisa 2018).}

### 2020-07-06 Tex/CAV2019/Trindade_Cordeiro_VSTTE2020_rev2.tex
revised Section 4
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

%---------------------------------------------------------------------------
\subsection{Optimization/Simulation Tools and Assumptions}
%---------------------------------------------------------------------------
Concerning the off-the-shelf optimization/simulation tools, only HOMER Pro performs an off-grid system with battery backup analysis and includes economical analysis. Here we used HOMER Pro version $3.13.1$ as a state-of-the-art optimization tool for comparison purposes. In particular, HOMER Pro has the following characteristics:
(a) it is available only for MS-Windows, its annual standard subscription costs US\$ $504.00$~\cite{HOMER}; 
(b) it has two optimization algorithms: one algorithm simulates all of the feasible system configurations defined by the search space, and additionally, a proprietary derivative-free algorithm to search for the least-costly system;
(c) it does not have LCC cost in its reports, only Net Present Cost (NPC); however, we can obtain LCC from NPC; 
(d) the optimization analysis defines a load curve and temperature according to data collected from online databases. However, to allow a correct comparison, the curve load and the temperature were defined the same as our synthesis approach; 
(e) it does not have a charge controller. During the tests, we have chosen the ``load-following'' option, which produces enough power to meet the demand~\cite{HOMER} and (usually) presents a non-overestimated solution; 
(f) it was assumed 95\% availability of the PV system. By definition, ``availability'' is the percentage of time at which a power system can feed the load requirements~\cite{Khatib2014}. For an ordinary house electrical load, 95\% is considered acceptable;
(g) it was assumed a string of two batteries to match the voltage of the system of $24$ V DC, which was used for our automated synthesis tool; 
(h) it was included a generic flat-plate PV of $1$ kW and generic lead-acid batteries of $1$ kW ($83.4$ Ah capacity). During run-time, HOMER decides the size in kW of each one based on feasibility and lower cost.

In order to validate and compare the optimal sizing solution produced by our approach and by HOMER Pro, we use a simulation tool, called PVsyst version $6.86$~\cite{PVsyst}, with plenty of commercial equipment in its data bank. We have considered a comparison for an entire year's weather data of simulation to guarantee that the proposed sizing meets the electrification requirements. PVsyst is a PC software package developed by a Swiss company used for the study, sizing, simulation, and data analysis of solar PV systems. PVsyst contains design, sizing, 3D shading scene, simulation, grid, and off-grid features. It uses comprehensive irradiation data from Meteonorm\footnote{https://meteonorm.com/en/}, and aging analysis~\cite{PVsyst2017}. However, it does not perform optimization; therefore, PVsyst needs the system sized to validate it. Furthermore, PVsyst does not have commercial inverter equipment and, as a result, does not consider surge power demand as the ones produced by air conditioners and refrigerators for a few seconds. PVsyst is a commerical software with $30$-day test possibility and runs only in MS-Windows.

@@

All experiments regarding the verification tools were conducted on an otherwise idle Intel Xeon CPU E5-4617 ($8$-cores) with $2.90$ GHz and $64$ GB RAM, running Ubuntu $16.04$ LTS $64$-bits. For HOMER Pro, we have used an Intel Core i5-$4210$ ($4$-cores) with $1.7$ GHz and $4$ GB RAM running Windows 10. The ideal scenario would be to use the same hardware configuration for the experiments. However, we faced restrictions concerning the license for the HOMER Pro tool; besides, we did not have the autonomy to change the Linux VM machine installed in the servers of our university due to the internal policy. This has an impact on performance, which is less favourable to HOMER Pro. PVsyst used the same configuration as HOMER Pro. We perform the experiments with a predefined \textit{time out} of $660$ minutes.

%The hardware platform was not the same because of the availability of the machines;

@@

The results are presented in Table~\ref{tab1}. 
%
\begin{table}
\caption{Case studies and results: optimization of stand-alone PV systems.}\label{tab1}
\begin{scriptsize}
\begin{tabular}{c|c|c|c|c}
\hline
\hline
Tools & \makecell{CBMC 5.11 \\(MiniSat 2.2.1)}& \makecell{ESBMC 6.0.0 \\(Boolector 3.0.1)}& \makecell{CPAchecker 1.8\\(MathSAT 5.5.3)}& HOMER Pro 3.13.1\\
\hline
\hline
Specification & Result & Result & Result & Result \\
\hline
\makecell{\textbf{Case Study 1}\\Peak:342W\\Surge:342W \\E:3,900Wh/day\\Autonomy:48h} & OM & \makecell{SAT (620 min) \\NTP:6$\times$330W (2P-3S)\\NBT:16$\times$105Ah (2S-8P)\\Controller 35A/145V\\Inverter 700W/48V\\LCC: US\$ 10,214.04} & \makecell{SAT (548 min) \\NTP:6$\times$330W (2P-3S)\\NBT:16$\times$105Ah (2S-8P)\\Controller 35A/145V\\Inverter 700W/1600W/48V\\LCC: US\$ 10,214.04} & \makecell{(Time: 0.33 min)\\2.53 kW of PV\\NBT:12$\times$83.4Ah (2S-6P)\\0.351kW inverter\\LCC: US\$ 7,808.04}\\
\hline
\makecell{\textbf{Case Study 2}\\Peak:814W\\Surge:980W\\E:4,880Wh/day\\Autonomy:48h} & OM & TO & TO & \makecell{(Time: 0.18 min)\\3.71 kW of PV\\NBT:20$\times$83.4Ah (2S-10P)\\0.817kW inverter\\LCC: US\$ 12,861.75} \\
\hline
\makecell{\textbf{Case Study 3}\\Peak:815W\\Surge:980W\\E:4,880Wh/day\\Autonomy:12h} & OM & \makecell{SAT (63 min) \\NTP:14$\times$150W (7P-2S)\\NBT:6$\times$105Ah (2S-3P)\\Controller 35A/145V\\Inverter 1,200W/48V\\LCC: US\$ 9,274.07} & TO & Not possible \\
\hline
\makecell{\textbf{Case Study 4}\\Peak:253W\\Surge:722W\\E:3,600Wh/day\\Autonomy:48h} & OM & \makecell{SAT (147 min) \\NTP:6$\times$330W (2P-3S)\\NBT:16$\times$105Ah (2S-8P)\\Controller 35A/145V\\Inverter 280W/48V\\LCC: US\$ 9,678.63} & \makecell{SAT (605 min) \\NTP:6$\times$330W (2P-3S)\\NBT:16$\times$105Ah (2S-8P)\\Controller 35A/145V\\Inverter 280W/48V\\LCC: US\$ 9,678.63} & \makecell{(Time: 0.23 min)\\2.42 kW of PV\\NBT:12$\times$83.4Ah (2S-6P)\\0.254kW inverter\\LCC: US\$ 7,677.95}\\
\hline
\makecell{\textbf{Case Study 5}\\Peak:263W\\Surge:732W\\E:2,500Wh/day\\Autonomy:48h} & OM & \makecell {SAT (36.70 min) \\NTP:4$\times$330W (2S-2P)\\NBT:14$\times$80Ah (2S-7P)\\Controller 35A/145V\\Inverter 280W/24V \\LCC: US\$ 8,900.70} & \makecell {SAT (254.25 min) \\NTP:4$\times$330W (2S-2P)\\NBT:14$\times$80Ah (2S-7P)\\Controller 35A/145V\\Inverter 280W/24V \\LCC: US\$ 8,900.70} & \makecell{(Time: 0.18 min)\\1.59 kW of PV\\NBT:10$\times$83.4Ah (2S-5P)\\0.268kW inverter\\LCC: US\$ 6,175.57} \\
\hline
\makecell{\textbf{Case Study 6}\\Peak:322W\\Surge:896W\\E:4,300Wh/day\\Autonomy:48h} & OM & \makecell {SAT (380.93 min) \\NTP:6$\times$320W (2P-3S)\\NBT:18$\times$105Ah (2S-9P)\\Controller 35A/145V\\Inverter 400W/24V \\LCC: US\$ 10,136.61} & TO & \makecell{(Time: 0.22 min)\\3.15 kW of PV\\NBT:14$\times$83.4Ah (2S-7P)\\0.328kW inverter\\LCC: US\$ 9,112.45} \\
\hline
\makecell{\textbf{Case Study 7}\\Peak:1,586W\\Surge:2,900W\\E:14,000Wh/day\\Autonomy:48h} & OM & UNSAT (0.48 min) & TO & \makecell{(Time: 0.20 min)\\12.5 kW of PV\\NBT:66$\times$83.4Ah (2S-33P)\\1.60kW inverter\\LCC: US\$ 41,878.11} \\
\hline
\hline
\end{tabular}
\\Legend: OM = out of memory; TO = time out; IF = internal failure; E = energy;    NTP = total number of panels, NBtotal = total number of batteries, NPS = number of panels in series; NPP = number of panels in parallel, NBS = number of batteries in series; NBP = number of batteries in parallel; LCC = Life Cycle Cost.
\end{scriptsize}
\end{table}
%
The violation (SAT result) indicated all over the Table~\ref{tab1} 
is the $assert$ of the line $18$ in Algorithm~\ref{alg:opt-algorithm} and indicates that an optimal solution was found.
Here, CBMC was unable to produce any conclusive result. \textit{Out of memory} situations occurred in all case studies.

@@

Here we used ESBMC in incremental mode with Boolector; ESBMC was able to reach the optimal sizing of case studies $1$, $3$, $4$, $5$, and $6$ with a FAIL/ SAT response, varying from $36$ minutes to $10$ hours. ESBMC, with this configuration, was unable to obtain an optimal solution in cases $2$ and $7$. Case $2$ produced a \textit{time out}. Moreover, case $7$ resulted in a UNSAT result, i.e., ESBMC was unable to provide a feasible solution. However, this is not a bug, and it means that the available list of equipment can not produce a feasible solution that satisfies electrical compatibility or design requirements. This UNSAT situation was reached in less than one minute. These experimental results answer the \textit{EG2}.

HOMER Pro was able to evaluate six case studies (cases $1$, $2$, $4$, $5$, $6$, and $7$) under $30$ seconds; it was much faster than the proposed automated synthesis tool (cf.~\textit{EG3}). Case study $3$ could not be simulated since HOMER Pro does not have the battery autonomy adjustment feature, i.e., the tool always tries to feed the given load with electricity $365$ days/year. Some HOMER Pro drawbacks were also noted. (1) System equipment does not include an explicit charge controller. HOMER Pro includes a controller automatically to simulate the charge/discharge of batteries and to meet the load requirement. However, without costs or even with electrical characteristics such as maximum current and voltage, which are common during PV sizing. (2) HOMER Pro requires the inclusion of some battery specification to initiate optimization; however, it does not change the electrical specifications during simulation; the results presented are multiples of the original battery type suggested by the user. For example, it was started with a $83.4$ Ah lead-acid battery, and during simulation, HOMER Pro did not try to use other capacities or types. (3) HOMER Pro does not present the optimal solution in terms of connections of PV panel arrays, just the total in terms of power, i.e., it presents neither the models and the power of each PV panel nor the total of panels in series or parallel.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Comparison Between Formal Synthesis and HOMER Pro}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
If we compare the results of the formal synthesis against those of HOMER Pro, we observed some distinct results in terms of the technical solution and cost (cf. Table~\ref{tab1}). Concerning the performance, there exists a vast difference in favor of HOMER Pro that obtained the results in considerably less time: few seconds in the opposite of an average of $4$ hours for the automated synthesis technique.
%
Particularly in the case of LCC, the cost varied from $11$\% to $44$\%, producing a higher estimation from the automated synthesis technique. However, considering that the cost of individual items of each database used to compose the optimal design is not the same among the tools, it is plausible to obtain distinct results.

On the one hand, concerning the PV panels sizing, the results presented by the automated synthesis were smaller in terms of power than the ones produced by the simulation tool. The difference varied from $19$\% to $65$\%. On the other hand, concerning the battery bank, the results were smaller in terms of capacity for HOMER Pro. The difference was between $34$\% to $68$\%. The mathematical models are different and particular parameters can be tuned for each technique, and that can justify the difference, which was presented in all the case studies.

Those discrepancies are not easy to address without some real systems validation. However, we use the simulation software PVsyst to validate the optimal sizing produced, as shown in Table~\ref{tab2}. Note that PVsyst has a pre-sizing feature, which presents a minimum recommended sizing of PV panels and batteries (only), but without using manufacturers' data or models for it. This feature was used as reference mainly with HOMER Pro, where there exists no equipment brands or models (only power and capacities specification). PVsyst was used with the field-deployed and the formal synthesis sizing solutions, where brands and models were simulated in PVsyst according to the sized system.

\begin{table}
\caption{Optimal sizing validation with PVsyst.}
\label{tab2}
\begin{scriptsize}
\begin{tabular}{c|c|c|c|c}
\hline
\hline
CS & \makecell{PVsyst\\(pre-sizing)}& \makecell{Field\\deployed\\validation}& \makecell{Formal synthesis\\sizing\\validation}& \makecell{HOMER Pro\\sizing\\validation}\\
\hline
\hline
CS 1 & \makecell{P= 1,166 W\\B= 381 Ah\\(minimum)} & \makecell{Not correct sizing \\Avail. $<$ 95\%\\(91.06\%)} & \makecell{No error found \\100\% of avail.} & \makecell{No error found\\Panels oversized in 2.16 $\times$\\Batteries oversized in 1.39 $\times$}\\
\hline
CS 2 & \makecell{P= 1,482 W\\B= 478 Ah\\(minimum)} & \makecell{NA\\There exists no real PV system\\available for comparison} & \makecell{NA \\(TO result\\in Table~\ref{tab1})} & \makecell{No error found\\Panels oversized in 2.6 $\times$\\Batteries oversized in 1.74 $\times$}\\
\hline
CS 3 & \makecell{Not possible to \\simulate\\(autonomy $<$ 24h)} & \makecell{NA\\There exists no real PV system\\available for comparison} & \makecell{Only technique that\\produced solution} & \makecell{NA\\(autonomy $<$ 24h)}\\
\hline
CS 4 & \makecell{P= 1,078 W\\B= 354 Ah\\(minimum)} & \makecell{No error found \\95.76\% of avail.} & \makecell{No error found \\97.37\% of avail.} & \makecell{No error found\\Panels oversized in 2.24 $\times$\\Batteries oversized in 1.41 $\times$}\\
\hline
CS 5 & \makecell{P= 823 W\\B= 268 Ah\\(minimum)} & \makecell{No error found \\100\% of avail.} & \makecell{No error found \\100\% of avail.} & \makecell{No error found\\Panels oversized in 1.93 $\times$\\Batteries oversized in 1.56 $\times$}\\
\hline
CS 6 & \makecell{P= 1,299 W\\B= 421 Ah\\(minimum)} & \makecell{Not correct sizing \\Avail. $<$ 95\%\\(85.65\%)} & \makecell{No error found \\100\% of avail.} & \makecell{No error found\\Panels oversized in 2.42 $\times$\\Batteries oversized in 1.38 $\times$}\\
\hline
CS 7 & \makecell{P= 4,263 W\\B= 1,384 Ah\\(minimum)} & \makecell{NA\\There exists no real PV system\\available for comparison} & \makecell{NA \\(UNSAT result\\in Table~\ref{tab1})} & \makecell{No error found\\Panels oversized in 2.9 $\times$\\Batteries oversized in 1.99 $\times$}\\
\hline
\hline
\end{tabular}
\\Legend: CS = case study; NA = sizing not available for validation; B = batteries capacity; P = panels power; Avail.= Availability (expected of 95\% or greater as a design requirement).
\end{scriptsize}
\end{table}

Each simulation with PVsyst took $4$ seconds. We were unable to validate case study $3$ using PVsyst since the battery autonomy is less than 24 hours, and only the proposed synthesis technique can perform the optimal sizing (PVsyst and HOMER Pro are limited for a $24$ h minimum). Case studies $2$ and $7$ had only HOMER Pro sizing validation, because there exists no deployed equivalent system in the field, and the synthesis technique did not present a solution due to \textit{time out} and internal failures in the underlying verification engine. %(our technique presented a \textit{time out} in case study $2$ and an \textit{UNSAT} in the case study $7$).

Overall, those comparisons among our approach, the optimization software, and the deployed systems, with validation through simulation tool, show that the synthesis solution is sound and complete, which answers \textit{EG1} and {EG3}.

HOMER Pro suggests a value in kW for the inverters that are very close to the maximum load of every case study, but it is not a commercial value. The proposed synthesis tool, however, presents inverters that are commercial and can be obtained off-the-shelf. Moreover, our synthesis approach considers surge power demand from the house, which is not considered by HOMER Pro or PVsyst. This feature is a definite advantage of the formal synthesis method. HOMER Pro does not include charge controllers as a specific item of equipment in its mathematical model; only the synthesis tool presents a commercial controller and includes it during the cost analysis. The formal synthesis method, therefore, presents more reliable results than HOMER Pro.

In summary, our synthesis technique can present a solution that is far more detailed and closer to commercial conditions than the solution presented by HOMER Pro. In particular, the automated synthesis method can provide all the details of every component of a PV system solution, with complete electrical details from the manufacturer datasheet, including the model of the component, nominal current, and voltage. In this respect, even the name of the manufacturer can be cited (in Table~\ref{tab1}, it was removed to avoid unauthorized advertising). Moreover, the validation through PVsyst simulation, using the PV sizing produced by HOMER Pro and our synthesis approach, shows that our results are feasible and not as oversized as HOMER Pro results, mainly concerning PV panels.

\textcolor{blue}{Worth to mention that an optimal solution from a tool is not necessarily the same optimal from other tool, mainly when the data base of equipment items (with different costs) are not the same. Therefore the comparison must take this issue into account.}

>>>>

%---------------------------------------------------------------------------
\subsection{Optimization/Simulation Tools and Assumptions}
%---------------------------------------------------------------------------
Concerning the off-the-shelf optimization/simulation tools, only HOMER Pro performs an off-grid system with battery backup analysis and includes economical analysis. Here we used HOMER Pro version $3.13.1$ as a state-of-the-art optimization tool for comparison purposes. In particular, HOMER Pro has the following characteristics:
(a) it is available only for MS-Windows, its annual standard subscription costs US\$ $504.00$~\cite{HOMER}; 
(b) it has two optimization algorithms: one algorithm simulates all of the feasible system configurations defined by the search space, and additionally, a proprietary derivative-free algorithm to search for the least-costly system;
(c) it does not have LCC cost in its reports, only Net Present Cost (NPC); however, we can obtain LCC from NPC; 
(d) the optimization analysis defines a load curve and temperature according to data collected from online databases. However, to allow a correct comparison, the curve load and the temperature were defined the same as our synthesis approach; 
(e) it does not have a charge controller. During the tests, we have chosen the ``load-following'' option, which produces enough power to meet the demand~\cite{HOMER} and (usually) presents a non-overestimated solution; 
(f) it was assumed 95\% availability of the PV system. By definition, ``availability'' is the percentage of time at which a power system can feed the load requirements~\cite{Khatib2014}. For an ordinary house electrical load, 95\% is considered acceptable;
(g) it was assumed a string of two batteries to match the voltage of the $24$ V DC system, which was used for our automated synthesis tool; 
(h) it was included a generic flat-plate PV of $1$ kW and generic lead-acid batteries of $1$ kW ($83.4$ Ah capacity). During run-time, HOMER decides the size in kW of each one based on feasibility and lower cost.

To validate and compare the optimal sizing solution produced by our approach and by HOMER Pro, we use a simulation tool, called PVsyst version $6.86$~\cite{PVsyst}, with plenty of commercial equipment in its data bank. We have considered a comparison for an entire year's weather data of simulation to guarantee that the proposed sizing meets the electrification requirements. PVsyst is a PC software package developed by a Swiss company used for the study, sizing, simulation and data analysis of solar PV systems. PVsyst contains design, sizing, 3D shading scene, simulation, grid, and off-grid features. It uses comprehensive irradiation data from Meteonorm,\footnote{https://meteonorm.com/en/} and aging analysis~\cite{PVsyst2017}. However, it does not perform optimization; therefore, PVsyst needs the system sized to validate it. Furthermore, PVsyst does not have commercial inverter equipment and, as a result, does not consider surge power demand as the ones produced by air conditioners and refrigerators for a few seconds. PVsyst is commercial software with a $30$-day test possibility and runs only in MS-Windows.

@@

All experiments regarding the verification tools were conducted on an otherwise idle Intel Xeon CPU E5-4617 ($8$-cores) with $2.90$ GHz and $64$ GB RAM, running Ubuntu $16.04$ LTS $64$-bits. For HOMER Pro, we have used an Intel Core i5-$4210$ ($4$-cores) with $1.7$ GHz and $4$ GB RAM running Windows 10. The ideal scenario would be to use the same hardware configuration for the experiments. However, we faced restrictions concerning the license for the HOMER Pro tool; besides, we did not have the autonomy to change the Linux VM machine installed in our university's servers due to the internal policy. This setup has an impact on performance, which is less favorable to HOMER Pro. PVsyst used the same configuration as HOMER Pro. We perform the experiments with a predefined \textit{time out} of $660$ minutes.

@@

The results are presented in Table~\ref{tab1}. 
%
\begin{table}
\caption{Case studies and results: optimization of stand-alone PV systems.}\label{tab1}
\begin{scriptsize}
\begin{tabular}{c|c|c|c|c}
\hline
\hline
Tools & \makecell{CBMC 5.11 \\(MiniSat 2.2.1)}& \makecell{ESBMC 6.0.0 \\(Boolector 3.0.1)}& \makecell{CPAchecker 1.8\\(MathSAT 5.5.3)}& HOMER Pro 3.13.1\\
\hline
\hline
Specification & Result & Result & Result & Result \\
\hline
\makecell{\textbf{Case Study 1}\\Peak:342W\\Surge:342W \\E:3,900Wh/day\\Autonomy:48h} & OM & \makecell{SAT (620 min) \\NTP:6$\times$330W (2P-3S)\\NBT:16$\times$105Ah (2S-8P)\\Controller 35A/145V\\Inverter 700W/48V\\LCC: US\$ 10,214.04} & \makecell{SAT (548 min) \\NTP:6$\times$330W (2P-3S)\\NBT:16$\times$105Ah (2S-8P)\\Controller 35A/145V\\Inverter 700W/1600W/48V\\LCC: US\$ 10,214.04} & \makecell{(Time: 0.33 min)\\2.53 kW of PV\\NBT:12$\times$83.4Ah (2S-6P)\\0.351kW inverter\\LCC: US\$ 7,808.04}\\
\hline
\makecell{\textbf{Case Study 2}\\Peak:814W\\Surge:980W\\E:4,880Wh/day\\Autonomy:48h} & OM & TO & TO & \makecell{(Time: 0.18 min)\\3.71 kW of PV\\NBT:20$\times$83.4Ah (2S-10P)\\0.817kW inverter\\LCC: US\$ 12,861.75} \\
\hline
\makecell{\textbf{Case Study 3}\\Peak:815W\\Surge:980W\\E:4,880Wh/day\\Autonomy:12h} & OM & \makecell{SAT (63 min) \\NTP:14$\times$150W (7P-2S)\\NBT:6$\times$105Ah (2S-3P)\\Controller 35A/145V\\Inverter 1,200W/48V\\LCC: US\$ 9,274.07} & TO & Not possible \\
\hline
\makecell{\textbf{Case Study 4}\\Peak:253W\\Surge:722W\\E:3,600Wh/day\\Autonomy:48h} & OM & \makecell{SAT (147 min) \\NTP:6$\times$330W (2P-3S)\\NBT:16$\times$105Ah (2S-8P)\\Controller 35A/145V\\Inverter 280W/48V\\LCC: US\$ 9,678.63} & \makecell{SAT (605 min) \\NTP:6$\times$330W (2P-3S)\\NBT:16$\times$105Ah (2S-8P)\\Controller 35A/145V\\Inverter 280W/48V\\LCC: US\$ 9,678.63} & \makecell{(Time: 0.23 min)\\2.42 kW of PV\\NBT:12$\times$83.4Ah (2S-6P)\\0.254kW inverter\\LCC: US\$ 7,677.95}\\
\hline
\makecell{\textbf{Case Study 5}\\Peak:263W\\Surge:732W\\E:2,500Wh/day\\Autonomy:48h} & OM & \makecell {SAT (36.70 min) \\NTP:4$\times$330W (2S-2P)\\NBT:14$\times$80Ah (2S-7P)\\Controller 35A/145V\\Inverter 280W/24V \\LCC: US\$ 8,900.70} & \makecell {SAT (254.25 min) \\NTP:4$\times$330W (2S-2P)\\NBT:14$\times$80Ah (2S-7P)\\Controller 35A/145V\\Inverter 280W/24V \\LCC: US\$ 8,900.70} & \makecell{(Time: 0.18 min)\\1.59 kW of PV\\NBT:10$\times$83.4Ah (2S-5P)\\0.268kW inverter\\LCC: US\$ 6,175.57} \\
\hline
\makecell{\textbf{Case Study 6}\\Peak:322W\\Surge:896W\\E:4,300Wh/day\\Autonomy:48h} & OM & \makecell {SAT (380.93 min) \\NTP:6$\times$320W (2P-3S)\\NBT:18$\times$105Ah (2S-9P)\\Controller 35A/145V\\Inverter 400W/24V \\LCC: US\$ 10,136.61} & TO & \makecell{(Time: 0.22 min)\\3.15 kW of PV\\NBT:14$\times$83.4Ah (2S-7P)\\0.328kW inverter\\LCC: US\$ 9,112.45} \\
\hline
\makecell{\textbf{Case Study 7}\\Peak:1,586W\\Surge:2,900W\\E:14,000Wh/day\\Autonomy:48h} & OM & UNSAT (0.48 min) & TO & \makecell{(Time: 0.20 min)\\12.5 kW of PV\\NBT:66$\times$83.4Ah (2S-33P)\\1.60kW inverter\\LCC: US\$ 41,878.11} \\
\hline
\hline
\end{tabular}
\\Legend: OM = out of memory; TO = time out; IF = internal failure; E = energy;  NTP = total number of panels, NBtotal = total number of batteries, NPS = number of panels in series; NPP = number of panels in parallel, NBS = number of batteries in series; NBP = number of batteries in parallel; LCC = Life Cycle Cost.
\end{scriptsize}
\end{table}
%
The violation (SAT result) indicated in Table~\ref{tab1} is the $assert$ of the line $18$ in Algorithm~\ref{alg:opt-algorithm} and suggests that an optimal solution was found.
Here, CBMC was unable to produce any conclusive result; \textit{out of memory} situations occurred in all case studies.

@@

Here we used ESBMC in BMC incremental mode with Boolector; ESBMC was able to reach the optimal sizing of case studies $1$, $3$, $4$, $5$, and $6$ with a FAIL/ SAT response, varying from $36$ minutes to $10$ hours. ESBMC, with this configuration, was unable to obtain an optimal solution in cases $2$ and $7$. Case $2$ produced a \textit{time out}. Moreover, case $7$ resulted in a UNSAT result, i.e., ESBMC was unable to provide a feasible solution. However, this is not a bug, and it means that the available list of equipment can not produce a feasible solution that satisfies electrical compatibility or design requirements. This UNSAT situation was reached in less than one minute. These experimental results answer the \textit{EG2}.

HOMER Pro was able to evaluate six case studies (cases $1$, $2$, $4$, $5$, $6$, and $7$) under $30$ seconds; it was much faster than the proposed automated synthesis tool (cf.~\textit{EG3}). Case study $3$ could not be simulated since HOMER Pro does not have the battery autonomy adjustment feature, i.e., the tool always tries to feed the given load with electricity $365$ days/year. Some HOMER Pro drawbacks were also noted. (1) System equipment does not include an explicit charge controller. HOMER Pro includes a controller automatically to simulate the charge/discharge of batteries and to meet the load requirement. However, without costs or even with electrical characteristics such as maximum current and voltage, which are common during PV sizing. (2) HOMER Pro requires the inclusion of some battery specification to initiate optimization; however, it does not change the electrical specifications during simulation; the results presented are multiples of the original battery type suggested by the user. For example, it was started with an $83.4$ Ah lead-acid battery, and during simulation, HOMER Pro did not try to use other capacities or types. (3) HOMER Pro does not present the optimal solution in terms of connections of PV panel arrays, just the total in terms of power, i.e., it presents neither the models and the power of each PV panel nor the total of panels in series or parallel.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Comparison Between Formal Synthesis and HOMER Pro}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

If we compare the formal synthesis results against those of HOMER Pro, we observed some distinct effects in terms of the technical solution and cost (cf. Table~\ref{tab1}). Concerning the performance, there exists a vast difference in favor of HOMER Pro that obtained the results in considerably less time: few seconds in the opposite of an average of $4$ hours for the automated synthesis technique. Particularly in the case of LCC, the cost varied from $11$\% to $44$\%, producing a higher estimation from the automated synthesis technique. However, considering that the cost of individual items of each database used to compose the optimal design is not the same among the tools, it is plausible to obtain distinct results.

On the one hand, concerning the PV panels sizing, the results presented by the automated synthesis were smaller in terms of power than the ones produced by the simulation tool. The difference varied from $19$\% to $65$\%. On the other hand, concerning the battery bank, the results were smaller in terms of HOMER Pro capacity. The difference was between $34$\% to $68$\%. The mathematical models are different and particular parameters can be tuned for each technique, and that can justify the difference, which was presented in all the case studies.

Those discrepancies are not easy to address without some real systems validation. However, we use the simulation software PVsyst to validate the optimal sizing produced, as shown in Table~\ref{tab2}. Note that PVsyst has a pre-sizing feature, which presents a minimum recommended sizing of PV panels and batteries (only), but without using manufacturers' data or models for it. This feature was used as reference mainly with HOMER Pro, where there exists no equipment brands or models (only power and capacities specification). PVsyst was used with the field-deployed and the formal synthesis sizing solutions, where brands and models were simulated in PVsyst according to the sized system.
%
\begin{table}
\caption{Optimal sizing validation with PVsyst.}
\label{tab2}
\begin{scriptsize}
\begin{tabular}{c|c|c|c|c}
\hline
\hline
CS & \makecell{PVsyst\\(pre-sizing)}& \makecell{Field\\deployed\\validation}& \makecell{Formal synthesis\\sizing\\validation}& \makecell{HOMER Pro\\sizing\\validation}\\
\hline
\hline
CS 1 & \makecell{P= 1,166 W\\B= 381 Ah\\(minimum)} & \makecell{Not correct sizing \\Avail. $<$ 95\%\\(91.06\%)} & \makecell{No error found \\100\% of avail.} & \makecell{No error found\\Panels oversized in 2.16 $\times$\\Batteries oversized in 1.39 $\times$}\\
\hline
CS 2 & \makecell{P= 1,482 W\\B= 478 Ah\\(minimum)} & \makecell{NA\\There exists no real PV system\\available for comparison} & \makecell{NA \\(TO result\\in Table~\ref{tab1})} & \makecell{No error found\\Panels oversized in 2.6 $\times$\\Batteries oversized in 1.74 $\times$}\\
\hline
CS 3 & \makecell{Not possible to \\simulate\\(autonomy $<$ 24h)} & \makecell{NA\\There exists no real PV system\\available for comparison} & \makecell{Only technique that\\produced solution} & \makecell{NA\\(autonomy $<$ 24h)}\\
\hline
CS 4 & \makecell{P= 1,078 W\\B= 354 Ah\\(minimum)} & \makecell{No error found \\95.76\% of avail.} & \makecell{No error found \\97.37\% of avail.} & \makecell{No error found\\Panels oversized in 2.24 $\times$\\Batteries oversized in 1.41 $\times$}\\
\hline
CS 5 & \makecell{P= 823 W\\B= 268 Ah\\(minimum)} & \makecell{No error found \\100\% of avail.} & \makecell{No error found \\100\% of avail.} & \makecell{No error found\\Panels oversized in 1.93 $\times$\\Batteries oversized in 1.56 $\times$}\\
\hline
CS 6 & \makecell{P= 1,299 W\\B= 421 Ah\\(minimum)} & \makecell{Not correct sizing \\Avail. $<$ 95\%\\(85.65\%)} & \makecell{No error found \\100\% of avail.} & \makecell{No error found\\Panels oversized in 2.42 $\times$\\Batteries oversized in 1.38 $\times$}\\
\hline
CS 7 & \makecell{P= 4,263 W\\B= 1,384 Ah\\(minimum)} & \makecell{NA\\There exists no real PV system\\available for comparison} & \makecell{NA \\(UNSAT result\\in Table~\ref{tab1})} & \makecell{No error found\\Panels oversized in 2.9 $\times$\\Batteries oversized in 1.99 $\times$}\\
\hline
\hline
\end{tabular}
\\Legend: CS = case study; NA = sizing not available for validation; B = batteries capacity; P = panels power; Avail.= Availability (expected of 95\% or greater as a design requirement).
\end{scriptsize}
\end{table}

Each simulation with PVsyst took $4$ seconds. We were unable to validate case study $3$ using PVsyst since the battery autonomy is less than 24 hours, and only the proposed synthesis technique can perform the optimal sizing (PVsyst and HOMER Pro are limited for a $24$ h minimum). Case studies $2$ and $7$ had only HOMER Pro sizing validation. There is no deployed equivalent system in the field, and the synthesis technique did not present a solution due to \textit{time out} and internal failures in the underlying verification engine. %(our technique presented a \textit{time out} in case study $2$ and an \textit{UNSAT} in the case study $7$).

Overall, those comparisons with our approach, the optimization software, and the deployed systems, with validation through simulation tool, show that the synthesis solution is sound and complete, which answers \textit{EG1} and {EG3}.

HOMER Pro suggests a value in kW for the inverters that are very close to the maximum load of every case study, but it is not commercial. The proposed synthesis tool, however, presents inverters that are commercial and can be obtained off-the-shelf. Moreover, our synthesis approach considers surge power demand from the house, which is not viewed by HOMER Pro or PVsyst. This feature is a definite advantage of the formal synthesis method. HOMER Pro does not include charge controllers as a specific item of equipment in its mathematical model; only the synthesis tool presents a commercial controller and includes it during the cost analysis. The formal synthesis method, therefore, presents more reliable results than HOMER Pro.

In summary, our synthesis technique can present a solution that is far more detailed and closer to commercial conditions than the answer given by HOMER Pro. In particular, the automated synthesis method can provide all the details of every component of a PV system solution, with complete electrical information from the manufacturer datasheet, including the model of the component, nominal current, and voltage. In this respect, even the name of the manufacturer can be cited (in Table~\ref{tab1}, it was removed to avoid unauthorized advertising). Moreover, the validation through PVsyst simulation, using the PV sizing produced by HOMER Pro and our synthesis approach, shows that our results are feasible and not as oversized as HOMER Pro results, mainly concerning PV panels.

\textcolor{blue}{Note that an optimal solution from a tool is not necessarily the same optimal from other tools, mainly when the database of equipment items (with different costs) are not the same. Therefore, the comparison must take this issue into account.}

%---------------------------------------------------------------------------
\subsection{Threats to validity} 
%---------------------------------------------------------------------------

We have reported a favorable assessment of the proposed method. Nevertheless, we have also identified four threats to the validity of our results that constitute future work. First, improvement of the power reliability analysis: to include loss of load probability or loss of power supply probability, which can make the study more accurate. Second, improvement of the system cost analysis by adding operational and maintenance costs to the adopted LCC analysis. Third, increase the equipment and manufacturers database: this will increase the optimization complexity, but the result will also allow improved sizing. Lastly, the underlying software verifiers employed here perform bit-precise verification based on the Floating-Point (FP) theory. We could use a real arithmetic strategy to tackle these equations; however, in this study, we have exploited the FP arithmetic, which is an approximation of the real one.
